---
title: "Weight of Fish"
author: "Estrella Aguilar"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
require(car)
Fish <- read.csv(file = "Fish.csv")
```

# Predicting Fish Weight

```{r}
Perch <- filter(Fish,Species=="Perch")
Perch <- select(Perch, -Species)
```


```{r}
PerchModel1<- lm(Weight~.,Perch)
summary(PerchModel1)
```


```{r}
PerchModel2<- lm(Weight~. -Length1,Perch)
summary(PerchModel2)
```


```{r}
PerchModel3<- lm(Weight~. -Length1 -Length2,Perch)
summary(PerchModel3)
```



```{r}
PerchModel4<- lm(Weight~. -Length1 -Length2 -Length3,Perch)
summary(PerchModel4)
```

```{r}
PerchModel5<- lm(Weight~. -Length1 -Length2 -Length3 -Width,Perch)
summary(PerchModel5)
```


```{r}
regsubsets.out <- regsubsets(Weight~., data=Perch, nbest=1, nvmax=NULL, force.in=NULL, force.out=NULL,
    method="exhaustive")
summary.out <- summary(regsubsets.out)
```

```{r}
library(leaps)
regsubsets.out <-
regsubsets(Weight ~ .,
data = Perch,
nbest = 1, # 1 best model for each number of predictors
nvmax = NULL, # NULL for no limit on number of variables
force.in = NULL, force.out = NULL,
method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```

### Best Models

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```
```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```
  
Interpreting our results we see that the best two element models is using height and width. The best overall model is also the 2 element model using height and width using adjusted R squared. 
   

## Pike

```{r}
Pike <- filter(Fish,Species=="Pike")
Pike <- select(Pike, -Species)
```





```{r}
library(leaps)
regsubsets.out <-
regsubsets(Weight ~ .,
data = Pike,
nbest = 1, # 1 best model for each number of predictors
nvmax = NULL, # NULL for no limit on number of variables
force.in = NULL, force.out = NULL,
method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

Interpreting our results we see that the best two element models is using Length 1 and Length 3. The best overall model is the 5 element model using adjusted R squared. 

### Best Models

### Best Two regressor model

## Roach
```{r}
Roach <- filter(Fish,Species=="Roach")
Roach <- select(Roach, -Species)
```


### Best Models

```{r}
library(leaps)
regsubsets.out <-
regsubsets(Weight ~ .,
data = Roach,
nbest = 1, # 1 best model for each number of predictors
nvmax = NULL, # NULL for no limit on number of variables
force.in = NULL, force.out = NULL,
method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

Interpreting our results we see that the best two element models is using Length3 and width . The best overall model is also the 2 element model using Length3 and width using adjusted R squared.



## Final Summary Statements

I learned how to use leaps and learned how to start codes from scratch removing statements until I got the best adjusted R squared model. 
  
